ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-23 docs/paper/paper.tex
Updated background section

3D, short for the three dimensions of space we experience, is a catch-all term used to describe the varied technologies used to create virtual worlds. The technology stack for 3D can be roughly split into two broad categories \emph{asset creation} and \emph{asset scripting}. Asset creation \ref{sec:assetcreation} is the process of creating virtual objects, scenes, and materials. Asset scripting \ref{sec:assetscripting} is the process of controlling those assets and their behavior over time. Both of these technologies require human expertise and artistic talent \ref{sec:humanexpertise}.

@@

Assets are digital representations of a 3D object. In the engineering and manufacturing world, assets are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}. In the entertainment industry, assets are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}. Modeling and CAD are two different words for the same thing: deciding the connectivity and placement of a graph of points, also called vertices, which define the surface of an object. Vertices are connected by edges, and a closed loop creates a polygon known as a face. Many 3D assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras. Finally, asset creation also encompasses the process of material creation. The appearance of a virtual object is determined by a material, which may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions.

@@

There is a fourth dimmension to our reality which is time. Asset scripting is the process of defining the behavior of assets and scenes over the dimmension of time. One such process is called animation, which consists of an expert human artist pupeteering and deforming a mesh frame by frame to create the illusion of natural movement. Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) are often used to record the movement of real objects and play those movements back on virtual assets.

Game Engines are software tools which allow for manipulation of assets in a more structured and systematic way by providing software interfaces to control the virtual world. Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}. These game engines allow for rule-based spawning, animation, and complex interactions between assets in the virtual world.

\subsubsection{Human Expertise}
\label{sec:humanexpertise}

Houdini \citep{houdini} and Blender \citep{blender}

\subsection{Deep Learning}
\label{sec:deeplearning}

Modern deep learning can be implemented in a variety of programming languages including Python, R, Julia, Scala, Ruby, Octave, MATLAB, and even C/C++. Amongst these, Python has emerged as the lingua franca, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}.

>>>>

3D, short for the three dimensions of space we live in, is a catch-all term used to describe the varied technologies used to create virtual worlds. The technology stack for 3D can be roughly split into two broad categories: \emph{asset creation} and \emph{asset scripting}. Asset creation \ref{sec:assetcreation} is the process of creating assets: virtual objects, scenes, and materials. Asset scripting \ref{sec:assetscripting} is the process of manipulating those assets and their interactions over the fourth dimension of time. Decades of progress have resulted in sophisticated software tools that make 3D workflows easier and more automated, but a significant amount of human expertise and artistic talent is still required.

@@

Assets are digital representations of a 3D object. One type of asset is a mesh: a connected graph of 3D points, also called vertices, which define the surface of an object. Vertices are interconnected by edges, and a closed loop of vertices creates a polygon known as a face. In the engineering and manufacturing world, meshes are created using computer aided design (CAD) software such as AutoCAD \citep{autocad}, Solidworks \citep{solidworks}, Onshape \citep{onshape}, and Rhino \citep{rhino}. In the entertainment industry, meshes are created using modeling software such as Maya \citep{maya}, 3DSMax \citep{3dsmax}, and Cinema4D \citep{cinema4d}.

Whereas a mesh describes the shape and form of an object, a material asset describes the texture and appearance of a virtual object. A material may define rules for the reflectivity, specularity, and metallic-ness of the object as a function of lighting conditions. Materials are used by shader programs to calculate the exact pixel values to render for each face of a mesh polygon. Modeling software will usually come packaged with tools that allow the creation and configuration of materials.

Finally, asset creation also encompasses the process of scene composition. Assets can be organized into scenes, which may contain other unique virtual objects such as simulated lights and cameras. Deciding where to place assets, especially lights, is still almost entirely done by hand. Automatic scene composition remains an outstanding challenge in the 3D technology stack.

@@

The fourth perceivable dimension of our reality is time. Asset scripting is the process of defining the behaviors of assets within scenes over time. One type of asset scripting is called animation, which consists of creating a set of sequential mesh deformations to create the illusion of natural movement. Animation is a tedious manual task since every frame must be defined: expert animators spend decades honing their digital puppeteering skills. Specialized software is often used to automate this task as much as possible, and technologies such as Motion Capture (MoCap) can be used to record the movement of real objects and play those movements back on virtual assets.

Game Engines are software tools which allow for asset scripting in a more structured and systematic way, mostly by providing software interfaces (e.g. code) to control the virtual world. Used extensively in the video game industry after which they were named, examples include Unity \citep{unity3d}, Unreal Engine \citep{unrealengine}, GoDot \citep{godot}, and Roblox \citep{roblox}. These game engines allow for rule-based spawning, animation, and complex interactions between assets in the virtual world. Programming within game engines is a separate skillset to modeling and animating and is usually done by separate engineers within an organization.

\subsubsection{Blender}
\label{sec:blender}

Blender is an open source 3D software tool originally released in 1994 \citep{blender}. It has grown steadily over the decades and has become one of the most popular 3D tools available, with a massive online community of users. Blender strength in its breadth: it provides simple tools for every part of the 3D workflow, rather than specializing in a narrow slice of the 3D workflow. Organizations such as game studios have traditionally preferred specialization, having separate teams of engineers using separate tools, such as Maya for modeling and Unreal Engine for scripting. However, the convenience of using a single tool, combined with the advantage of a single engineer being able to see a project start to finish, make a strong case for Blender as the ultimate winner in the 3D software tools race. By focusing on open source and community, Blender continues to gain adoption as more and more of the world’s new 3D developers choose to learn Blender over other more specialized tools.

In addition to encompassing the full breadth of the 3D workflow, Blender has the unique strength of using Python as the programming language of choice for asset scripting. Python has emerged as the lingua franca for modern deep learning, rising to the top in part due to the popularity of open source frameworks such as TensorFlow \citep{tensorflow}, PyTorch \citep{pytorch}, and Scikit-Learn \citep{scikit-learn}. If we wish for Machine Learning Engineers to perform asset scripting, they will be much more comfortable in Blender’s Python environment compared to the C# of Unity or the C++ of Unreal Engine.
